---
title: "Practice in R"
author: "Ru"
date: "2/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RSelenium)
library(xml2)
library(rvest)
library(dplyr)
library(purrr)
```

Goals for the week:
Using RSelenium: 
  >Open chrome in a web browser --done
  >Navigate to a certain page and open it  -- done
  > Find the search element --done. I used CSS selectors 
    >Input a 5-digit zipcode -- done. I used 01063
  > Search -- done. used the RSelenium code 
    > 10 results should pop up  -- done 
    > Find a way to put these in a data frame  -- still working. 
  > Click next  -- done 

#Find a way to get the doctors' information: Combining RSelenium and rvest 
```{r}
remDr <- remoteDriver(remoteServerAddr = "localhost",
                      port = 4445L,
                      browserName = "chrome")
remDr$open()
# remDr$navigate("http://www.google.com")

url = "https://my.uscis.gov/findadoctor"

#First step: Opening chrome in a web browser, and navigating to our page
rD <- rsDriver(port = 4445L, browser = "chrome", version = "latest", chromever = "latest", geckover = "latest", verbose = TRUE)
   remDr <- rD[["client"]]
   #navigate to the webpage 
   remDr$navigate(url)
   
   
   #find the search bar where we put in zipcode
   zipElem <- remDr$findElement("css selector","#form_data_search_location")
   #let RSelenium type in the zipcode and search 
   zipElem$sendKeysToElement(list("01063","\uE007")) 
   
   #"\uE007" is the key for "ENTER"
?rsDriver
```

#scrape using rvest

```{r}
doctors = xml2::read_html(remDr$getPageSource()[[1]])%>%
  rvest::html_nodes(".name")%>%
  rvest::html_text(trim = TRUE)%>%
  dplyr::data_frame(doctor_name = .)
doctors
#rvest::html_nodes(".name")

#html_text(doctors) %>% purrr::map_int(nchar) == 0

test = xml2::read_html(remDr$getPageSource()[[1]]) %>%
       html_nodes(".doctor-name") %>%
       html_text(trim = TRUE) %>%
       dplyr::data_frame(test = .)
View(test)

doctor_test <-xml2::read_html(remDr$getPageSource()[[1]]) %>%
  html_nodes(".doctor-name") %>%
  html_text(trim = TRUE)
```

```{r}
#if statement to scrape medical facilities with multiple doctors
ifelse(xml2::read_html(remDr$getPageSource()[[1]])%>%
  rvest::html_nodes(".name")%>%
  rvest::html_text(trim = TRUE)%>% purrr::map_int(nchar) == 0,
  doctor_test<-xml2::read_html(remDr$getPageSource()[[1]]) %>%
  html_nodes(".doctor-name") %>%
  html_text(trim = TRUE),
  doctor_help<-xml2::read_html(remDr$getPageSource()[[1]])%>%
    rvest::html_nodes(".name")%>%
    rvest::html_text(trim = TRUE))
doctor_test
doctor_help

 
  xml2::read_html(remDr$getPageSource()[[1]]) %>%
  html_nodes(".doctor-name col-span-8") %>%
  html_text(trim = TRIM) %>%
  dplyr::data_frame(test = .)
  print("Im done")

  
#  find: class = doctors-div
#  doctor-name col-span-8
#  doctor-telephone
```

```{r}
address <- xml2::read_html(remDr$getPageSource()[[1]])%>%
  html_nodes(".address_top")%>%
  html_text(trim = TRUE)%>%
  dplyr::data_frame(address = .)
city <- xml2::read_html(remDr$getPageSource()[[1]])%>%
  html_nodes(".address_bottom")%>%
  html_text(trim = TRUE)%>%
  dplyr::data_frame(city = .)
phone <- xml2::read_html(remDr$getPageSource()[[1]])%>%
  html_nodes(".telephone")%>%
  html_text(trim = TRUE)%>%
  dplyr::data_frame(phone_number = .)
##example
phone

scrapeddf <- data.frame(doctors, address,city)

uscisdf <- scrapeddf[!scrapeddf$doctor_name=="",]
uscisdf <- data.frame(uscisdf, phone)
```

```{r}

```


#on to the next button ...
```{r}
#find what css selector the 'NEXT' button uses 
nextBtn <- remDr$findElement("css selector","#populated_addresses > div:nth-child(11) > div > div.next > button")
class(nextBtn)
#click the next button
nextBtn$clickElement()

#while loops
```

#Is it reading doctors 11-21? 
```{r}
#scrape the next page
doc = xml2::read_html(remDr$getPageSource()[[1]])%>%
  rvest::html_nodes(".name")%>%
  rvest::html_text(trim = TRUE)%>%
  dplyr::data_frame(doctor_name = .)
doc
```


#close and stop the server
```{r}
remDr$close()
   # stop the selenium server
   rD[["server"]]$stop()
```

#Next steps:
  1. Try piecing the two together in a function. This step will involve many other steps. 
  2. See if you can use the div class "col-span-10" to just scrape everything at once(I tried it once and it's returning rows not columns)
  3. Create a for-loop 
  

